---
title: "AS3-2: 股市動態"
author: "第 9 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
#讀取
IBM <- read.csv("data/IBMStock.csv")
GE <- read.csv("data/GEStock.csv")
ProcterGamble <- read.csv("data/ProcterGambleStock.csv")
CocaCola <- read.csv("data/CocaColaStock.csv")
Boeing <- read.csv("data/BoeingStock.csv")
library(dplyr)

nrow(IBM)

```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
#
Boeing$date_d<- as.Date(Boeing$Date, format = "%m/%d/%y")
CocaCola$date_d<- as.Date(CocaCola$Date, format = "%m/%d/%y")
GE$date_d<- as.Date(GE$Date, format = "%m/%d/%y")
IBM$date_d<- as.Date(IBM$Date, format = "%m/%d/%y")
ProcterGamble$date_d<- as.Date(ProcterGamble$Date, format = "%m/%d/%y")
min(CocaCola$date_d)

Boeing$date_y <- format(Boeing$date_d, "%Y") %>%  as.numeric()
#
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
#
max(Boeing$date_d)
max(CocaCola$date_d)
#
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
#
mean(IBM$StockPrice)
#
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
#
min(GE$StockPrice)
#
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice) ### 146.6
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice) ### 44.88
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice) ### 18.19
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
CocaCola$Date <- as.Date(CocaCola$Date,format="%m/%d/%y")
plot(CocaCola$Date, CocaCola$StockPrice, type="l")
### min 1973
### max 1980
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(Boeing$date_d,Boeing$StockPrice)
plot(CocaCola$date_d,CocaCola$StockPrice)
plot(GE$date_d,GE$StockPrice)
plot(IBM$date_d,IBM$StockPrice)
plot(ProcterGamble$date_d,ProcterGamble$StockPrice)
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
subset(Boeing,date_d == "1984-01-01","StockPrice") - subset(Boeing,date_d == "1983-01-01","StockPrice")
subset(CocaCola,date_d == "1984-01-01","StockPrice") - subset(CocaCola,date_d == "1983-01-01","StockPrice")
subset(GE,date_d == "1984-01-01","StockPrice") - subset(GE,date_d == "1983-01-01","StockPrice") 
subset(IBM,date_d == "1984-01-01","StockPrice") - subset(IBM,date_d == "1983-01-01","StockPrice") 
subset(ProcterGamble,date_d == "1984-01-01","StockPrice") 
-subset(ProcterGamble,date_d == "1983-01-01","StockPrice")
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#

#
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
a <- subset(Boeing, date_d >= "2000-01-01" & date_d <= "2000-12-01")
plot(a$date_d,a$StockPrice)
#
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#
subset(Boeing, StockPrice == max(Boeing$StockPrice))
subset(CocaCola, StockPrice == max(CocaCola$StockPrice))
subset(GE, StockPrice == max(GE$StockPrice))
subset(IBM, StockPrice == max(IBM$StockPrice))
subset(ProcterGamble, StockPrice == max(ProcterGamble$StockPrice))

#
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
stock_Boeing <- subset(Boeing, date_d >= "1997-09-01" & date_d <= "1997-11-01")
#直接找出該月份的索引值
which(Boeing$date_d == "1997-09-01")
Boeing$StockPrice[c(333:335)]
CocaCola$StockPrice[c(333:335)]
GE$StockPrice[c(333:335)]
IBM$StockPrice[c(333:335)]
ProcterGamble$StockPrice[c(333:335)]
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
which(Boeing$date_d == "2004-01-01")
which(Boeing$date_d == "2005-12-01")
Boeing$StockPrice[c(409:432)] %>% plot
CocaCola$StockPrice[c(409:432)] %>% plot
GE$StockPrice[c(409:432)] %>% plot
IBM$StockPrice[c(409:432)] %>% plot
ProcterGamble$StockPrice[c(409:432)] %>% plot
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
IBM$date_m <- format(IBM$date_d, "%m") %>%  as.numeric()
tapply(IBM$StockPrice, IBM$date_m, mean) > mean(IBM$StockPrice)
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
GE$date_m <- format(GE$date_d, "%m") %>%  as.numeric()
which.max(tapply(GE$StockPrice,GE$date_m,mean))
CocaCola$date_m <- format(CocaCola$date_d, "%m") %>%  as.numeric()
which.max(tapply(CocaCola$StockPrice,CocaCola$date_m,mean))
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
ProcterGamble$date_m <- format(ProcterGamble$date_d, "%m") %>%  as.numeric()
Boeing$date_m <- format(Boeing$date_d, "%m") %>%  as.numeric()
subset(CocaCola, date_m == 1, "StockPrice")

tapply(Boeing$StockPrice,Boeing$date_m,mean)[12] > tapply(Boeing$StockPrice,Boeing$date_m,mean)[1]

tapply(CocaCola$StockPrice,CocaCola$date_m,mean)[12] > tapply(CocaCola$StockPrice,CocaCola$date_m,mean)[1]

tapply(GE$StockPrice,GE$date_m,mean)[12] > tapply(GE$StockPrice,GE$date_m,mean)[1]
                                                                                
tapply(IBM$StockPrice,GE$date_m,mean)[12] > tapply(IBM$StockPrice,GE$date_m,mean)[1]

tapply(ProcterGamble$StockPrice,GE$date_m,mean)[12] > tapply(ProcterGamble$StockPrice,GE$date_m,mean)[1]
```

<br><br><br>

