---
title: "期中競賽"
author: "第 9 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---



```{r}
library(readr)
library(dplyr)
library(d3heatmap)
library(ggplot2)

C <- read_csv("Group9/brazilian-ecommerce/olist_customers_dataset.csv")
Lo <- read_csv("Group9/brazilian-ecommerce/olist_geolocation_dataset.csv")
It <- read_csv("Group9/brazilian-ecommerce/olist_order_items_dataset.csv")
pay <- read_csv("Group9/brazilian-ecommerce/olist_order_payments_dataset.csv")
re <- read_csv("Group9/brazilian-ecommerce/olist_order_reviews_dataset.csv")
order <- read_csv("Group9/brazilian-ecommerce/olist_orders_dataset.csv")
prod <- read_csv("Group9/brazilian-ecommerce/olist_products_dataset.csv")
sell <- read_csv("Group9/brazilian-ecommerce/olist_sellers_dataset.csv")
categ <- read_csv("Group9/brazilian-ecommerce/product_category_name_translation.csv")

```


```{r}
unique(order$order_id) %>% length()    ### 99441 different order
unique(order$customer_id) %>% length()  ### 99441 customer ID
duplicated(order$customer_id) %>% table()  ### false 99441
order$order_id %in% re$order_id %>% table() ### TRUE

###

re$review_id %>% duplicated() %>% table() ### TRUE 827, FALSE 99173
re$order_id %>% duplicated() %>% table() ### TRUE 559, FALSE 99441
unique(re$order_id) %>% length() ### 99441
setdiff(unique(re$order_id),unique(order$order_id)) ### character(0)
duplicated(C[,c(1,2)]) %>% table()

###

order$customer_id %>% unique() %>% length() ### 99411 
C$customer_unique_id %>% unique() %>% length() ### 96096
C$customer_unique_id %>% table %>% table()

#     1     2     3     4     5     6     7     9    17 
# 93099  2745   203    30     8     6     3     1     1 

C[,c(4, 5)] <- lapply(C[,c(4, 5)], factor) 
summary(C)
C$customer_city %>% table() %>% sort %>% tail(10)

# sao bernardo do campo             guarulhos              salvador          porto alegre              campinas 
#                  938                  1189                  1245                  1379                  1444 
# curitiba              brasilia        belo horizonte        rio de janeiro             sao paulo 
#     1521                  2131                  2773                  6882                 15540 

### 

setdiff(unique(pay$order_id),unique(order$order_id)) ### character(0)
setdiff(unique(order$order_id),unique(pay$order_id)) ### "bfbd0f9bdef84302105ad712db648a6c"

pay$payment_type <- as.factor(pay$payment_type)
unique(pay$order_id) %>% length() ### 99440

pay$order_id %>% table() %>% table() 
pay$payment_sequential %>% table() %>% sum() ### 103886
#     1     2     3     4     5     6     7     8     9    10    11    12    13    14    15    19    21    22    26    29 
# 96479  2382   301   108    52    36    28    11     9     5     8     8     3     2     2     2     1     1     1     1 

pay[pay$payment_sequential == 2,]$order_id %in% pay[pay$payment_sequential == 1,]$order_id %>% table()

# FALSE  TRUE 
#    80  2959 

summary(pay)

# order_id         payment_sequential      payment_type   payment_installments   payment_value  
# Length:103886      Min.   : 1.00      boleto     :19784   Min.   : 0.00        Min.   :    0  
# Class :character   1st Qu.: 1.00      credit_card:76795   1st Qu.: 1.00        1st Qu.:   57  
# Mode  :character   Median : 1.00      debit_card : 1529   Median : 1.00        Median :  100  
#                    Mean   : 1.09      not_defined:    3   Mean   : 2.85        Mean   :  154  
#                    3rd Qu.: 1.00      voucher    : 5775   3rd Qu.: 4.00        3rd Qu.:  172  
#                    Max.   :29.00                          Max.   :24.00        Max.   :13664  
# 

### It

It$order_id %>% unique() %>% length() ### 98666 
It$order_id %in% order$order_id %>% table() ### TRUE

order$order_id %in% It$order_id %>% table() ### TRUE 98666 , FALSE 775

It$order_id %>% table() %>% table() 

#     1     2     3     4     5     6     7     8     9    10    11    12    13    14    15    20    21 
# 88863  7516  1322   505   204   198    22     8     3     8     4     5     1     2     2     2     1 

It[It$order_item_id == 2,]$order_id %in% It[It$order_item_id == 1,]$order_id %>% table() ### TRUE

# TRUE 
# 9803 

It$product_id %>% unique() %>% length() ### 32951
It$seller_id %>% unique() %>% length() ### 3095

### 

prod$product_id %>% unique() %>% length() ### 32951
setdiff(unique(It$product_id), unique(prod$product_id)) ### character(0)
prod$product_category_name %>% unique() %>% length() ### 74

###
categ$product_category_name %>% unique() %>% length() ### 71
setdiff(unique(prod$product_category_name), unique(categ$product_category_name))
### NA , "pc_gamer" , "portateis_cozinha_e_preparadores_de_alimentos"


###


Z = It %>% group_by(seller_id) %>% summarise(
  ItemsSold = n(),
  Rev = sum(price),
  noProd = n_distinct(product_id),
  avgPrice = mean(price),
  maxPrice = max(price),
  minPrice = min(price),
  avgFreight = mean(freight_value),
  avgRevProd = Rev/noProd,
  avgItemsProd = ItemsSold/noProd
)
summary(Z)


###


X = unique(It[,c(1,4)]) %>% left_join(re[,2:3]) %>% 
  group_by(seller_id) %>% summarise(
    noReview = n(),
    avgScore = mean(review_score),
    minScore = min(review_score),
    maxScore = max(review_score)) 

###

Z = Z %>% left_join(X) %>% left_join(sell)

```


```{r}
pacman::p_load(dplyr, FactoMineR, factoextra)
```

```{r}
ZZ <- Z[,c(1,2,3,4,5,8,9,10,11,12,15,16,17)]
```



```{r}

library(readr)
library(dplyr)
library(d3heatmap)
library(ggplot2)
library(caTools)
## library(chorddiag)
set.seed(1234)
ZZ$grp = kmeans(scale(ZZ[,c(3,5,6,9,10)]),5)$cluster %>% factor
ZZ$grp %>% table()


```

```{r}
# Z$group = factor(cutree(hc, k=4))
# 
# fviz_dend(
#   hc, k=8, show_labels=F, rect=T, rect_fill=T,
#   labels_track_height=0,
#   palette="ucscgb", rect_border="ucscgb")
```


```{r}
pacman::p_load(dplyr, FactoMineR, factoextra)
pca = PCA(ZZ[,c(3,5,6,9,10)])

```

```{r}
fviz_pca_ind(pca)
```




```{r}
grp <- ZZ$grp

fviz_pca_biplot(
  pca, repel=T, col.var="black", 
  col.ind=grp, alpha.ind=0.6, pointshape=16)
```



```{r}
# grp <- ZZ$grp
# 
# fviz_pca_biplot(
#   pca, repel=T, col.var="black", 
#   col.ind=grp, alpha.ind=0.6, pointshape=16, 
#   addEllipses = TRUE, ellipse.level = 0.6, mean.point = FALSE)

```


```{r}
group_by(ZZ, grp) %>% summarise(
  REV=mean(Rev), 
  avgPrice=mean(avgPrice), 
  avgFreight=mean(avgFreight),
  noReview=mean(noReview),
  avgScore=mean(avgScore),
  size=n() )
```

```{r}
### 價格高的顧客願意等？？？
```

```{r}
ZZZ<- ZZ[,c(3,5,6,9,10)]
colMeans(ZZZ)
ZA<- scale(ZZZ) %>% data.frame

par(cex=0.8)
split(ZA, grp) %>% sapply(colMeans) %>% barplot(beside=T,col=rainbow(5))
legend('topright',legend=colnames(ZZZ),fill=rainbow(5))
```




```{r}
load("~/Downloads/II.RData")
```

```{r}
II2 <- II %>% filter(grp== 1|grp == 4| grp== 2)
II2$grp <- II2$grp %>% as.numeric() %>% as.factor()
table(II2$grp, II2$category) %>% as.data.frame.matrix %>% 
  d3heatmap(F,F,col=cm.colors(13)[3:13])
```


```{r}

table(II$category)
table(II$grp, II$category) %>% as.data.frame.matrix %>% 
  d3heatmap(F,F,col=cm.colors(13)[3:13])

```

```{r}
## II %>% group_by(grp) 
II4 <- II %>% filter(grp == 3)

II4$category %>% table %>% sort(decreasing = TRUE) 

# auto          garden_tools         health_beauty        sports_leisure       furniture_decor 
#   13                    12                    10                     8                     7 
# baby computers_accessories     home_appliances_2              pet_shop            cool_stuff 
#                     6                     6                     6                     6                     5 

```




```{r}
R <- re
R2 <- R[,c(2, 4, 5)] 
R2 <- left_join(R2, I[,c(1,4)])
R2 <- left_join(R2[,c(4,1,2,3)], ZZ[,c(1,14)])

```


```{r}
R21 <- R2 %>% filter(grp == 1)

```


```{r}
library(rvest)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)

docs <- Corpus(VectorSource(R21$review_comment_message))
                                         # 將內容以語料庫形式儲存

```

```{r}

docs <- tm_map(docs, content_transformer(tolower)) 
docs <- tm_map(docs, removeNumbers)     #移除數字
docs <- tm_map(docs, removeWords,stopwords("portuguese")) # 移除常見的轉折詞彙
docs <- tm_map(docs, removePunctuation) #移除標點符號
docs <- tm_map(docs, stripWhitespace)  # 移除額外的空白

```


```{r}

dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d<- data.frame(word=names(v), freq=v)
head(d,50)

```

```{r}
wordcloud(words=d$word,freq=d$freq,min.freq=2,
                     max.words=150,random.order=FALSE,rot.per=0.35,
                     colors=brewer.pal(35,"Dark2"))

```


```{r}
Lo$geolocation_lat <- round(Lo$geolocation_lat,3)
Lo$geolocation_lng <- round(Lo$geolocation_lng,3)
```


```{r}
unique(sell$seller_zip_code_prefix) %>% length() ### 2246
names(Lo)[1] <- "seller_zip_code_prefix"
sell$seller_zip_code_prefix %>% unique() %>% length() 
sell_lo <- left_join(sell, Lo, by = "seller_zip_code_prefix")

```

```{r}
sell_lo2 <- sell_lo %>%  group_by(seller_id, seller_zip_code_prefix,  geolocation_state) %>% summarise(lat = mean(geolocation_lat), lng = mean(geolocation_lng))
sell_lo2 <- sell_lo2[!duplicated(sell_lo2$seller_id),]
sell_lo2 <- left_join(sell_lo2, ZZ[,c(1, 5, 10, 14)])

table(sell_lo2$grp)
```


```{r}
library(lubridate)
library(Imap)
library(maps)
Brazil <- map_data("world")%>%filter(region=="Brazil")
```

```{r}
ggplot() +
  geom_polygon(data = Brazil, aes(x= long, y= lat, group= group), fill="black")+
  geom_point(data= sell_lo2 , aes(x= lng, y= lat, color= grp), size = 2, alpha = 0.2)

```

```{r}
sell_lo22 <- sell_lo2 %>% filter(grp== 5)
ggplot() +
  geom_polygon(data = Brazil, aes(x= long, y= lat, group= group), fill="black") + geom_point(data= sell_lo22,aes(x= lng, y= lat, color= grp), size = 2, alpha = 0.2)

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

